PLANETESIMAL ACCRETION AT SHORT ORBITAL PERIODS

### 2023-04-28 refereeResponse.txt

7. Summary and Discussion
933: I would think the gravitational feedback still operates, just on a timescale that is much longer than the planetesimal accretion timescale that depletes the planetesimal supply.
	Agreed. We have changed 'does not operate' to 'does not a play a significant role'.
942: Refer to the section where this is discussed.
	Done
946: alpha is already reviewed in the paragraph above
	The last sentence of the previous paragraph (which mentions alpha) has been removed.
952: non-negligible is not very precise . Maybe change to while "alpha close to unity"
	'Non-negligible' has been changed to 'alpha close to unity'
954: Refer to figure where this is shown. I think Fig.2? Also "the same" is very strong. Maybe "very similar" instead.
	A reference to figure 2 has been added here. 'The same' has been has been changed to 'very similar'.
959: Sentence is currently implying that the boundary location is set by the distance to the star which doesn't really work in my opinion. Maybe just delete "and therefore the location of the boundary between these accretion modes" as this becomes clear with the subsequent sentence anyways.
	Done
965: I think this is too strong a statement. See my previous comments. I think the subsequent sentence "Although [...]" is more appropriate.
	We have changed 'is independent' to 'does not strongly depend'.
972: Refer to Fig. 10.
	A reference has been added to figures 9 and 10.
978: Missing a verb, maybe "differs" ? Also the second part of the sentence "along with [...]" seems odd to me. Maybe rephrase it in two sentences?
	The first sentence of this paragraph has been split into two parts.
986: Is there a reference for this? It does not seem obvious to me. See my previous comments.
	See figure 8 of Leinhardt 2015. The majority of constructive collisions are partial accretion events. A reference has been added to this in the text.
996: what bulk density? Maybe also rephrase to a less strong statement, e.g., "[...] bulk density, our results suggest that the boundary is located around 5 days in orbital period."
	Rocky material should have a bulk density of 3 g/cc. This is now specified in the text. The statement about the boundary location has been made less strong as per the referee's suggestion.
998: I recommend introducing a subsection heading here, for clarity.
	A subsection heading referencing satellitesimal accretion has been added
999: Maybe add references of what values for alpha typically were used?
	There aren't many planetesimal accretion papers that mention \alpha, but Lithwick 2014 is one that specifically assumes that \alpha << 1 for their calculations. We have mentioned that here.
1000: This sentence is somewhat odd to me. Yes, alpha = 1 are the largest bodies stable under tidal gravity, however, this applies not just to circumplanetary disks but also for the circumstellar planetesimals the authors investigated in their work. Because of this, it doesn't seem like this statement is an appropriate segue to circumplanetary disks. I suggest separating this paragraph as a subsection under a heading such as "high-alpha accretion in circumplanetary disks".
1003: delete "small"
	Done
1007: Can the authors clarify the relevance of the inclusion of spiral density wave interactions?
	The point here is that there are some additional dynamical mechanisms at play in these moon formation simulations. At least near the Roche limit, this is a distinctly non-local process, unlike the accretion modes that we demonstrated in this paper. Some extra clarification has been added to the text here.
1018: I recommend defining R_U for readers unfamiliar with Ida et al 2020, e.g., by summarizing that Ida et al 2020 considered a circumplanetary disk around Uranus.
	Since it is only mentioned in one place, we have replaced R_U with 'planetary radii'.
